Liveness-Based Garbage Collection for Lazy Languages

### 2015-07-11 paper/paper.tex
tables rewritten
Added proof of correctness

\bibliography{fun_hra}{}
\bibliographystyle{abbrv}
\end{document}

@@

A few observations: First observe that the transitions  which involving dereferencing and can lead to \bang are those which have a $H(\rho(x))$ term in their premise for some variable $x$.

>>>>

\bibliography{fun_hra}{}
\bibliographystyle{abbrv}
%\end{document}

@@

We observe that  the transitions involving dereferencing  and can lead
to \bang are those which have  a $H(...)$ term in the transition rule.
Of these most  of the terms are of the  form $H(\rho(x))$, involving a
root variable.  There is exactly  one occurrence of $H(l)$ which means
dereferencing using a heap location.

In both  the cases  we show  that the dereferencing  cannot lead  to a
\bang\ state in a function call less program.

For this we need the following lemma,
\begin{lemma}
\label{lem:correctness}
Consider, 
\begin{enumerate}
\item
 A \LET\ definition $\pi_i:(\LET~x \leftarrow~s~\IN~e)$ such
that there is  an evaluation path in $e$ in  which $\pi_i$ is followed
by a  use i.e an  occurrence of $\pi_j:(\CAR\ x)$,  $\pi_j:(\CDR\ x)$,
$\pi_j:(+\ x\ y)$, $\pi_j:(\SIF\ x\ e1\ e2)$ or $\pi_j:(\SRETURN\ x)$
\item
 A \LET\ definition $\pi_i(\LET~z  \leftarrow~(\CONS~x~y)~\IN~e$, such that
 $e$ includes  an evaluation path in  which there is an  occurrence of
 $\pi_j: (\CAR~z)$ and $\pi_j$ follows $\pi_i$.
\end{enumerate},
the demand on $x$ is non-null between $\pi_i$ and $\pi_j$.
\end{lemma} 
\begin{proof}
In the first case it is clear  that at all points $\pi_k$ which occurs
in between $\pi_i$ and $\pi_j$, $x$  has non-null demand as $x$ is used
directly in a strict computation.

In the second case, it can be seen that the liveness of $x$ due to the
\CONS\ is $\bcar\sigma$, where $\sigma$ is the demand on $z$. $\sigma$
definitely  includes  the  demand  $\acar\alpha$ due  to  its  use  in
$\pi_j$, therefore the demand on $x$ is at least $\alpha$.

 Since we do not kill the liveness of any variable along an evaluation
 path, and all program points along  an evaluation path share the same
 liveness environment, at any point along the evaluation path $x$ will
 not be set to $\bot$.
\end{proof}

For a program  executing according to {\em minefield  semantics}, if a
\bang\ has to occur then some variable which is dereferenced along the
evaluation path  must be set to  $\bot$, between its creation  and use
points.  This can  only happen  if the  demand on  the variable  being
dereferenced  was null.  From  the  lemma~\ref{lem:correctness} it  is
clear that this cannot happen.

The rest  of the proof depends  on converting a program  with function
calls to an equivalent program without function calls for which we 
refer the user to~\cite{asati14lgc}.
